PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 0.8$

### 2014-11-18 qfenv_paper/qf_environment.tex
Figure edits

%We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}. The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CLASSIFYING QUIESCENT AND STAR-FORMING GALAXIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Karim:2011aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
\begin{equation}
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} \label{eq:qsfclass} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lie above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\citealt{Moustakas:2013aa} Figure 1.).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY ENVIRONMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure*}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2h25_thresh75_sdss_z0_05_0_12_primus_z0_21_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, height=0.5\textwidth}
     \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Each redshift panel is divided into three sections by the environment classification cutoffs (black veritcal lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$. The percentages of the redshift bin contained in the environment classifications are presented above the distribution. For example at $0.2 < z < 0.4$, $\apheight.0 \%$ of galaxies in the redshift bin are in low density environments while $35.0\%$ of galaxies in the redshift bin are in high density environments. We note that the significant difference between the SDSS distribution and the PRIMUS distribution above is due to the difference in stellar mass completeness limit imposed in our galaxy sample.}      \label{fig:envcount}
    \end{center}
\end{figure*}

>>>>

%We present the absolute magnitude ($M_{r}$) versus redshift for the galaxy sample (black squares) in Figure \ref{fig:targetEDP}. The left-most panel corresponds to the sample derived from the SDSS-{\em GALEX} data and the rest correspond to the target sample derived from the PRIMUS data divided in bins with $\Delta z \sim 0.2$. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% CLASSIFYING QUIESCENT AND STAR-FORMING GALAXIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Classifying Quiescent and Star-Forming Galaxies} \label{sec:sfq}
We now classify our mass complete galaxy sample into quiescent or star-forming using an evolving cut based on specific star-formation rate utilized in \cite{Moustakas:2013aa} Section 3.2. This classification method uses the star-forming (SF) sequence, which is the correlation between star-formation rate (SFR) and stellar mass in star-forming galaxies observed at least until $z \sim 2$ (\citealt{Noeske:2007aa, Karim:2011aa}). The PRIMUS sample displays a well-defined SF sequence within the redshift range of our galaxy sample. Using the power-law slope for the SF sequence from \cite{Salim:2007aa} (SFR $\propto \mathcal{M}^{0.65}$) and the minimum of the quiescent/star-forming bimodality, determined empirically, we obtain the following equation to classify the target galaxies (Equation 2 in \citealt{Moustakas:2013aa}):
\begin{equation}
\rm{log}(\rm{SFR}_{\rm{min}}) = -0.49 + 0.64 \rm{log}(\mathcal{M} - 10) +1.07(z-0.1), 
\end{equation} \label{eq:qsfclass} 
where $\mathcal{M}$ is the stellar mass of the galaxy. If the target galaxy SFR and stellar mass lie above Equation \ref{eq:qsfclass} we classify it as star-forming; if below, as quiescent (\citealt{Moustakas:2013aa} Figure 1.).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% GALAXY ENVIRONMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
  \begin{center}
    \leavevmode
    \epsfig{file=fig_envcount_cylr2_5h35_thresh75_sdss_z0_05_0_12_primus_z0_2_1_0_lowenv0_5_highenv3_0_primuszerr_masslimit_edgecut_histogram.png, width=0.45\textwidth}
    \caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges. A fixed cylindrical aperture of $R_{\rm{ap}} =\apradius\;\rm{Mpc}$ and $H_{\rm{ap}} = \apheight\; \rm{Mpc}$ is used to measure environment. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. For each redshift panel, galaxies with $n_{\mathrm{env}} < 0.5$ are in low density environments and galaxies with $n_{\rm{env}} > 3.0$ are in high density environment. We note that the significant difference among the SDSS distribution and the PRIMUS distributions above is due to the different stellar mass completeness limits imposed on each redshift bin of our galaxy sample.}      \label{fig:envcount}
     %\caption{Normalized distribution of environment measurements ($n_{\rm{env}}$) for our mass complete galaxy sample within the edges. The star-forming galaxies contribution to the distribution is colored blue and diagonally patterned. The contribution from quiescent galaxies is colored in red. Each redshift panel is divided into three sections by the environment classification cutoffs (black veritcal lines): low density environment $n_{\rm{env}} < 0.5$ and high density environment $n_{\rm{env}} > 3.0$. The percentages of the redshift bin contained in the environment classifications are presented above the distribution. For example at $0.2 < z < 0.4$, $\apheight.0 \%$ of galaxies in the redshift bin are in low density environments while $35.0\%$ of galaxies in the redshift bin are in high density environments. We note that the significant difference between the SDSS distribution and the PRIMUS distribution above is due to the difference in stellar mass completeness limit imposed in our galaxy sample.}      \label{fig:envcount}
    \end{center}
\end{figure}
